
Moooo... ( hi :) )
This binary distribution for Linux is compiled using web2c V6.0 (which is 
the most recent TeX distribution for UNIX(tm) system as of Feb 1994, I think).
Gcc version 2.5.5 was used with "-O2 -fomit-frame-pointer -m486" option,
on my 386/25 machine.

LaTeX is the most recent version, which is LaTeX2e (for more informations,
please read  "The LaTeX Companion" by Goosens/Mittlebach/Samarin - support 
LaTeX3 project by purchasing the book. Half of the royalty goes to this 
project).

Dvips is version 5.526a.  Default font resolution is 300dpi.
Edit the file, /usr/TeX/lib/texmf/dvips/config.ps properly if you
want to use other resolutions (ex 600dpi).
If proper PK fonts do not exist under /usr/TeX/lib/texmf/fonts directory,
MakeTeXPK will generate PK fonts of the required resolution under 
/usr/TeX/lib/texmf/fonts/tmp/pk.  Move those PK fonts to the appropriate place
(some directory under /usr/TeX/lib/texmf/fonts), if you are going to use 
them regularly.

I also compiled some other utilities such as : 
                      xdvi, dvi2tty, detex, tgrind, makeindex.
I believe that they are also the most recent versions as of Feb 94.

total 5529
   7 texMANI.gz
   3 texREAD.ME
 392 texams.taz
 936 texbin.taz
 163 texcm.taz
 681 texcmpk.taz
 781 texfont.taz
 434 texlibib.taz
1041 texlibmc.taz
 511 texlibms.taz
 432 texnfss2.taz
  80 texdoc.taz

Please refer to texMANI.gz file to see what is in each archive.
About 16M bytes of disk space is required to install.

NOTE : Do *not* set the environment variables such as XDVIFONTS,
       PKFONTS, and etc., unless they are *really* necessary.
       If you have to set them - you understand what you are doing -
       don't forget to add PK fonts directory of this this distribution
       to your environment variables (most people won't need to do this).
       Xdvi and dvips in this distribution work just fine without
       setting any environment variables in your shell.
       If xdvi still calls MakeTeXPK, check whether you are using the
       xdvi in this distribution.

Please send an e-mail to me (wjin@cs.uh.edu), if you find any problems
with this binary distribution or if you have suggestions.

Moooooo..... ( thank you  :) )

____   ____  ____ ______________________________________ (__) _________________
|  |   |  |  |  |  W. Woody Jin (wjin@cs.uh.edu)         (oo)      Moo...
|  |   |  |__|  |  Bovinetic Algorithm Design     o=======\/  I'm  a Cow Lover.
|  |   |        |  Dept. of Cowmooputer Science / |     ||   My wife  was born
\  |---|  |--|  |  University of Houston       *  ||w---||   in Cow year.  Mooo
 \____/|__|  |__| ________________________________^^    ^^_____________________
% nohup cat *flames* >& /dev/bull &
